Variation in gaze understanding across the life span: A process-level perspective

### 2023-06-09 paper/manuscript.Rmd
add gazemodel data adults; write magnet sections

---
title             : "Variation in gaze understanding across the life span: A process-level perspective"
shorttitle        : "modeling variation in gaze understanding"
author:

  - name          : "Julia Prein"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Abstract

keywords          : "social cognition, individual differences, gaze cues, cognitive modeling"
wordcount         : "xxx"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
library("tidyverse")
library("papaja")
theme_set(theme_classic())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load_data}
tango_lifespan <- readRDS("../data/tango-lifespan.rds")
tango_model <- readRDS("../data/tango-model.rds")
magnet <- readRDS("../data/magnet-data.rds")
```

@@

```{r dev_sample}
lifespan_sample <- tango_lifespan %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )
```

@@

The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), and `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls).

@@

<!-- Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r lifespan_sample$n_total` English-speakers with an average age of `r lifespan_sample$age_mean` years (SD = `r lifespan_sample$age_sd`, range = `r lifespan_sample$age_min` - `r lifespan_sample$age_max`, `r lifespan_sample$n_females` females). -->

@@

We used the TANGO task [@prein2022tango].
The task was presented as an interactive web application (see Figure \@ref(fig:fig1); live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .5 to .8 for the categorical task version and .7 to .8 for the continuous task version; @prein2022tango].

Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground.
Depending on the task version, the target either fell into a box (categorical task version) or behind a hedge (continuous task version).
The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
The target flight was covered so that participants could not see where the target landed.
Participants' task was to locate the target by tracking the agent's gaze.
They could respond by clicking or touching on the screen.

@@

The outcome measure depended on the task version.
In the continuous *hedge version*, we assessed imprecision defined as the absolute difference between the target center and the x coordinate of the participant's click.
In the discrete *box version*, we calculated the proportion of correct responses.

The randomization of the final target location also depended on the task version.
In the hedge version, the screen width was divided into ten bins, while exact coordinates within each bin were randomly generated during runtime.
In the box version, the target randomly landed in one of the boxes.
We adjusted the task difficulty according to participants' age: children were presented with five boxes while adults were presented with eight boxes.
Each bin/box, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.

(ref:figlab1) **Setup of the TANGO**. (A) Infrastructure for online testing. (i) Subjects aged 3 -- 99+ can participate. Data collection can take place anywhere: online, in kindergartens, or research labs. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure local servers. (B) Hedge version (continuous) of the gaze understanding task. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. (C) Box version (discrete) of the gaze understanding task. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.

```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics("../figures/magnet_procedure.png")
```

@@

In the in-person sample, children were tested on a tablet in a quiet room in their kindergarten.
An experimenter guided the child through the study.
Half of the sample completed the continuous task version, while the other half completed the discrete task version.

In the remote sample, children and teenagers received a personalized link to the study website.
Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding.
Webcam videos were recorded whenever consented and technically feasible, in order to monitor whether children and teenagers responded on their own.

In the remote sample for children from three to five years old, the family's presentation device determined the task version.
Whenever a touchscreen was available, the continuous task version was presented.
For families using a computer without touchscreen, the discrete task version was shown.
Here, children were asked to point to the screen while the caregivers should execute the clicking for their children.

The number of teenagers in our internal database for recruiting families substantially decreased by age.
To avoid small sample sizes, we decided to only employ the continuous task version for our 7- to 17-year-olds.
Hence, children aged 7 years+ completed the continuous task version, independently from their presentation device.

The remote adult sample was equally distributed across the two task versions.

@@

-   TODO: non-linear model for development

@@

-   model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
-   entwicklungsperspektive basierend auf model
-   dann prozess-ebene =\> magnet

# Non-social vector following

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>.

The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No. 2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
The research adheres to the legal requirements of psychological research with children in Germany.
Data were collected between February and March 2023.

-   gut, dass unser maß ind diff messen kann, das nutzen wir jetzt

-   zsmhang mit vector following, aber nicht redundant

-   perspective-taking auch, aber auch nicht relevant, nicht theory of mind score

-   diskutieren dass die maße auch nict ind diff maße sind

-   model vergleich: welche komponente stecken in gafo drin?,
    welchen beitrag liefern die um score zu erklären?
    welche wichtiger, tom oder nur perspective taking

-   magnet versuch das vector following zu isolieren.
    ist da noch was anderes außerhalb vector-following?

-   aggregierte messungen immer besser, nur indikatoren für konstrukt

>>>>

---
title: "Variation in gaze understanding across the life span: A process-level perspective"
shorttitle: "modeling variation in gaze understanding"
author:

  - name          : "Julia Prein"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"
    role          :
      - Conceptualization
      - Methodology
      - Software
      - Investigation
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    role          :
      - Conceptualization
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

  - name          : "Luke Maurits"
    affiliation   : "1"
    role          : 
      - Formal Analysis
      - Writing - Review & Editing

  - name          : "Annika Werwach"
    affiliation   : "1"
    role          :
      - Methodology
      - Investigation
      - Writing - Review & Editing

  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
    role          :
      - Supervision
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"  
authornote: |
abstract: |
  Abstract

keywords          : "social cognition, individual differences, gaze cues, cognitive modeling"
wordcount         : "xxx"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
library("tidyverse")
library("papaja")
library("kableExtra")

theme_set(theme_classic())
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

```{r lifespan_sample, include = T, out.width = "100%"}
lifespan_sample <- readRDS("../saves/lifespan_sample.rds")

lifespan_table <- lifespan_sample %>% 
  mutate(
    n = str_glue_data(., "{n_total} ({n_females} female)"), 
    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
  ) %>% 
  rename(
    `Age group` = age_group,
    `Age SD` = age_sd, 
    `Age mean` = age_mean
  ) %>% 
  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)

apa_table(lifespan_table)
```

@@

The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r lifespan_sample$n_total[lifespan_sample$age_group == "3"]` 3-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "3"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "3"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "3"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "3"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "3"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "4"]` 4-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "4"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "4"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "4"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "4"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "4"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "5"]` 5-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "5"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "5"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "5"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "5"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "5"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "6"]` 6-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "6"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "6"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "6"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "6"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "6"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "7"]` 7-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "7"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "7"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "7"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "7"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "7"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "8"]` 8-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "8"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "8"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "8"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "8"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "8"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "9"]` 9-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "9"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "9"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "9"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "9"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "9"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "10"]` 10-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "10"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "10"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "10"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "10"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "10"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "11"]` 11-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "11"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "11"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "11"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "11"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "11"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "12"]` 12-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "12"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "12"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "12"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "12"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "12"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "13"]` 13-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "13"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "13"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "13"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "13"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "13"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "14"]` 14-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "14"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "14"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "14"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "14"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "14"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "15"]` 15-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "15"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "15"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "15"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "15"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "15"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "16"]` 16-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "16"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "16"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "16"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "16"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "16"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "17"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "17"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "17"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "17"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "17"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "17"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "18"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "18"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "18"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "18"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "18"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "18"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "19"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "19"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "19"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "19"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "19"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "19"]` girls).

@@

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision. The sample included `r lifespan_sample$n_total[lifespan_sample$age_group == "20"]` 20- to 29-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "20"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "20"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "20"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "20"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "20"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "30"]` 30- to 39-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "30"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "30"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "30"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "30"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "30"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "40"]` 40- to 49-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "40"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "40"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "40"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "40"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "40"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "50"]` 50- to 59-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "50"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "50"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "50"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "50"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "50"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "60"]` 60- to 69-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "60"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "60"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "60"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "60"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "60"]` female), and `r lifespan_sample$n_total[lifespan_sample$age_group == "70"]` 70- to 79-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "70"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "70"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "70"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "70"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "70"]` female).

@@

We used the continuous version of the TANGO [@prein2022tango]. The task was presented as an interactive web application (see Figure \@ref(fig:fig1); live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>). The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; @prein2022tango].

Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground. The target then fell behind a hedge (continuous task version). The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center. In test trials, the target flight was covered so that participants could not see where the target landed. Participants' task was to locate the target by tracking the agent's gaze. They could respond by touching on the screen.

@@

The outcome measure was imprecision, defined as the absolute difference between the target center and the x coordinate of the participant's click. Target coordinates were randomly generated during runtime. Each target bin, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.

(ref:figlab1) **Setup of the TANGO and Magnet tasks**. (A) TANGO: Gaze understanding task. The agent stands in a window with the target in front of them. A hedge grows and covers the target. The target falls to a random location on the ground. The agent's eyes track the movement of the target. (B) Magnet task: non-social vector estimation.

```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics("../figures/procedure.png")
```

@@

Children and teenagers received a personalized link to the study website. Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding. Webcam videos were recorded whenever consented and technically feasible, in order to monitor whether children and teenagers responded on their own.

@@

@@

-   model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
-   entwicklungsperspektive basierend auf model
-   dann prozess-ebene = magnet

```{r gazemodel_sample}
gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
```

The sample included the `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` three- to five-year-old children and `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group == 18])` adults from our Lifespan study. For age distributions, see Participant section of the Lifespan Study.

out of convenience, we only used ... since developmental chnage was minimial in adutls we used ...

(ref:figlab3) **Gaze funnel**

```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
knitr::include_graphics("../figures/gazefunnel_combined.png")
```

# Components of gaze understanding

Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding. In this study, we sought to inquire whether there are any other cognitive processes outside vector-following that constitute gaze understanding. We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.

First, we aimed at isolating the vector-following part of the gaze understanding task. For this, we designed a new non-social vector estimation task that shared all crucial design features of the understanding task. Additionally, we administered a ToM task battery, comprising 4 tasks from the ToM scale by Wellman and Liu (2004) and two additional perspective-taking tasks.

Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks. This way, we can disentangle which components comprise gaze understanding. In this way, we can find out what contribution each component makes to explain gaze understanding.

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>. The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No. 2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. The research adheres to the legal requirements of psychological research with children in Germany. Data were collected between February and March 2023.

```{r magnet_sample}
magnet_sample <- readRDS("../saves/magnet_sample.rds")
```

Testing took place in kindergartens in Leipzig, Germany. The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r sum(magnet_sample$age_sd)`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).

Children were tested in a quiet room in their kindergarten. An experimenter guided the child through the study. Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects design. All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) gaze understanding task. Several reasons motivated the decision. First, we decided for a fixed order to be able to compare participant's performance straight-forwardly with each other. Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task, to tasks with personal interaction, back to a tablet task. Third, we showed the non-social vector estimation task before the gaze understanding task, so that participants would not be biased to interpret the presented stimuli as "eye- / "agent-like".

### Non-social vector estimation
